%-------------------------
% Resume in LateX
% Template Author : Sourabh Bajaj
% Template License : MIT
% 
% This resume is based on the Sourabh Bajaj LaTeX resume template.
% Original template: https://github.com/sb2nov/resume
% 
% Customized and filled out by: Natya Vidhan Biswas
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Natya Vidhan Biswas}} & Email: \href{mailto:natya@duck.com}{natya@duck.com}\\
  \href{https://natya.is-a.dev/}{natya.is-a.dev} & Mobile: \href{tel:+919718413051}{+91-97184-13051} \\
\end{tabular*}

%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
    {Python, JavaScript, SQL, C++}
    \resumeSubItem{Databases}
    {MongoDB, Supabase, SQLite}
    \resumeSubItem{Frameworks}
    {Flask, Next.js, Tailwind CSS, Selenium, Pygame}
    \resumeSubItem{DevOps}
    {Docker, k3s, Linux, Git}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Facts-n-Data}{Remote}
      {Software Development Intern}{Mar 2024 -- Apr 2025}
      \resumeItemListStart
        \resumeItem{E-Commerce Automation}
          {Built and maintained data scraping and automation tools across \textbf{Amazon}, \textbf{FirstCry}, and \textbf{Myntra}, enabling large-scale product data collection and analysis.}
        \resumeItem{Analytics \& Monitoring}
          {Developed scripts for \textbf{BSR tracking}, \textbf{search term analysis}, and \textbf{real-time stock monitoring} to drive data-informed business decisions.}
        \resumeItem{Internal Tooling}
          {Refactored legacy codebases for improved efficiency and built internal tools including \textbf{user authentication} systems and \textbf{employee management dashboards}.}
      \resumeItemListEnd

    \resumeSubheading
      {BLITZ, The Computer Science Society}{Keshav Mahavidyalaya, Delhi University}
      {Secretary}{Aug 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Web Development}
          {Designed and developed the \textbf{official society website} for both annual cycles, serving as the primary digital presence for events and announcements.}
        \resumeItem{Volunteer Management}
          {During flagship events, \textbf{managed all volunteers} on-ground. Assigned tasks, delegated responsibilities, and ensured smooth execution across all event verticals.}
        \resumeItem{Faculty Coordination}
          {Acted as the \textbf{primary liaison} between the society team and faculty, coordinating with professors to maintain clear and consistent communications.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Melbourne}{Melbourne, Australia (Remote)}
      {Machine Learning Engineer (Contract)}{Dec 2023}
      \resumeItemListStart
        \resumeItem{Multimodal Pipeline}
          {Built an end-to-end \textbf{multimodal Twitch analytics pipeline} processing video, audio, and live chat to produce minute-level \textbf{sentiment, toxicity, and emotion} signals for streamers and audiences.}
        \resumeItem{Computer Vision}
          {Implemented \textbf{GPU-accelerated face identity filtering} using \textbf{InsightFace} embeddings and cosine similarity to robustly isolate streamer face frames across VOD segments; classified emotions per-chunk with \textbf{DeepFace}.}
        \resumeItem{NLP \& Audio Analysis}
          {Integrated \textbf{faster-whisper} for speech transcription and engineered audio features (pitch, RMS loudness, bitrate). Built a multi-model scoring layer combining \textbf{GoEmotions}, \textbf{Detoxify}, and \textbf{HateSonar} for chat and transcript analysis.}
        \resumeItem{Tooling \& Infrastructure}
          {Productionized the system with a \textbf{CUDA-enabled Docker} environment; built a \textbf{Flask-based human-in-the-loop face embedding builder} to bootstrap per-streamer identity recognition for the CV pipeline.}
      \resumeItemListEnd

    \resumeSubheading
      {PM Shri Kendriya Vidhyalaya}{Vigyan Vihar, Delhi}
      {Publication Captain}{Apr 2023 -- Mar 2024}
      \resumeItemListStart
        \resumeItem{School Magazine}
          {Managed all entries and editorial coordination for the annual school magazine publication.}
        \resumeItem{School Blog}
          {Developed and maintained the \textbf{entire school blog}, serving as the primary platform for school news and student content.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{Planq} -- Exam Preparation Platform}{\href{https://planq.in}{Website} $|$ \href{https://github.com/planq-org/}{GitHub}}
      \resumeItemListStart
        \resumeItem{Question Bank}
          {Curated a database of \textbf{47,000+} previous year questions spanning \textbf{6 All-India entrance exams}, enabling comprehensive exam preparation.}
        \resumeItem{Smart Scheduling}
          {Implemented an \textbf{Anki-like spaced repetition} algorithm that schedules topics based on individual student performance and preparation analytics.}
        \resumeItem{Test Generation}
          {Built dynamic \textbf{test generation} and preparation analysis features to track student progress across subjects and difficulty levels.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Memoria} -- Self-Hostable AI Blog Engine}{\href{https://github.com/natyavidhan/memoria}{GitHub}}
      \resumeItemListStart
        \resumeItem{PDF Pipeline}
          {Engineered a pipeline to extract text and images from PDFs, generate captions using a \textbf{vision model}, and output clean \textbf{Markdown} posts.}
        \resumeItem{Architecture}
          {Designed as a self-hostable \textbf{AI blog engine} built with \textbf{Flask} and \textbf{Supabase} for easy deployment and content management.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{MongoDB Explorer} -- Desktop MongoDB Client}{\href{https://github.com/natyavidhan/mongo-explorer}{GitHub}}
      \resumeItemListStart
        \resumeItem{Desktop Client}
          {Built a lightweight desktop \textbf{MongoDB} client with \textbf{Python} and \textbf{DearPyGui} as an alternative to MongoDB Compass.}
        \resumeItem{Features}
          {Supports browsing databases, editing documents, running queries, managing indexes, \textbf{schema analysis}, and data import/export.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Donut Shop} -- Home Server Infrastructure}{}
      \resumeItemListStart
        \resumeItem{Cluster Setup}
          {Built a \textbf{2-node Linux cluster} in a \textbf{master-worker} configuration orchestrated with \textbf{k3s} and \textbf{Longhorn} for persistent storage.}
        \resumeItem{Services}
          {Deployed and managed \textbf{NAS}, media streaming (\textbf{Plex/Jellyfin}), \textbf{VPN}, and various containerized services.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Keshav Mahavidhyalaya, Delhi University}{Pitampura, Delhi}
      {Bachelor of Science in Computer Science; CGPA: 6.88 (Till 3rd Semester)}{Aug 2024 -- May 2028}
    \resumeSubheading
      {PM Shri Kendriya Vidhyalaya}{Vigyan Vihar, Delhi}
      {10+2, PCM; 88\%/73\%}{April 2012 -- March 2024}
  \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------------
\section{Achievements}
  \resumeSubHeadingListStart
    \resumeSubItem{Pariksha Pe Charcha 2024}
      {Presented AI project in front of the Hon'ble Prime Minister of India.}
    \resumeSubItem{Smart India Hackathon 2025}
      {Secured \textbf{1st Runner-Up} in the Internal Round at Keshav Mahavidyalaya, Delhi University.}
    \resumeSubItem{Brainwave 2.0 Hackathon (2026)}
      {Secured \textbf{3rd place} in the Hardware track and \textbf{8th overall} as Finalists at the 36-hour hackathon by Dept. of IT, DTU, in association with AIMS-DTU.}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}